Assessment of drought impact over land cover in continental Chile by the analysis of water supply and demand from the ERA5-Land and MODIS

### 2024-01-04 article/paper_drought_Chile2023.qmd
update for igarrs2023

@@

In this research, we aim to analyze the impact of drought on different types of land cover classes in continental Chile by combining environmental variables such as biomass productivity, and water demand and supply gathered from earth observation products. The specific objectives of the study are: i) to calculate multi-scalar drought indices for water demand and supply for 1981–2023; ii) to evaluate LULC change for 2001–2021 and its relation to drought indices; iii) to analyze the relationship of a proxy of biomass (zcNDVI) with drought indices; and iv) to assess if the observed changes in the drought indices are linked to the TWS.

@@

@@

::: {#fig-elephants layout-ncol=2 fig.pos='!ht'}
![](../output/figs/LC_pers80_per_macrozone.png){width="7cm"}

>>>>

      cite-style: number

@@

In this research, we aim to analyze the impact of drought on different types of land cover classes in continental Chile by combining environmental variables such as biomass productivity, and water demand and supply gathered from earth observation products. The specific objectives of the study are: i) to calculate multi-scalar drought indices for water demand and supply for 1981–2023; ii) to evaluate LULC change for 2001–2021 and its relation to drought indices; iii) to analyze the relationship of a proxy of biomass (zcNDVI) with drought indices; and iv) to assess if the observed changes in the drought indices are linked to TWS.

@@

For water supply and demand variabes, we used ERA5-Land [@Munoz2019], a reanalys dataset wich provides the evolution of land variables since 1950. It has a spatial resolution of 0.1°, hourly frequency and global coverage. We selected the variables for total precipitation, 2 meters temperature, and volumetric soil water layers between 0 and 100cm of depth (layer 1 to layer 3).

To derive a proxy of vegetation productivity, we used the product MOD13A3 collection 6.1 from MODIS [@Didan2015]. It provides vegetation indices (NDVI and EVI) at 1km of spatial resolution and monthly frequency.

@@

::: {#fig-elephants layout-ncol=1 fig.pos='!ht'}
![](../output/figs/LC_pers80_per_macrozone.png){width="7cm"}

### 2024-01-04 article/paper_drought_Chile2023.tex
update for igarrs2023

\begin{keyword}
    drought \sep land cover change \sep 
    satellite
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, boxrule=0pt, breakable, interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, sharp corners]}{\end{tcolorbox}}\fi

@@

In this research, we aim to analyze the impact of drought on different
types of land cover classes in continental Chile by combining
environmental variables such as biomass productivity, and water demand
and supply gathered from earth observation products. The specific
objectives of the study are: i) to calculate multi-scalar drought
indices for water demand and supply for 1981--2023; ii) to evaluate LULC
change for 2001--2021 and its relation to drought indices; iii) to
analyze the relationship of a proxy of biomass (zcNDVI) with drought
indices; and iv) to assess if the observed changes in the drought
indices are linked to the TWS.

@@

@@

\begin{minipage}[t]{0.47\linewidth}

@@

\end{minipage}%
%
\begin{minipage}[t]{0.53\linewidth}

>>>>

\begin{keyword}
    drought \sep land cover change \sep 
    satellite
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, frame hidden, borderline west={3pt}{0pt}{shadecolor}, interior hidden, boxrule=0pt, breakable, enhanced]}{\end{tcolorbox}}\fi

@@

In this research, we aim to analyze the impact of drought on different
types of land cover classes in continental Chile by combining
environmental variables such as biomass productivity, and water demand
and supply gathered from earth observation products. The specific
objectives of the study are: i) to calculate multi-scalar drought
indices for water demand and supply for 1981--2023; ii) to evaluate LULC
change for 2001--2021 and its relation to drought indices; iii) to
analyze the relationship of a proxy of biomass (zcNDVI) with drought
indices; and iv) to assess if the observed changes in the drought
indices are linked to TWS.

@@

For water supply and demand variabes, we used ERA5-Land
\citep{Munoz2019}, a reanalys dataset wich provides the evolution of
land variables since 1950. It has a spatial resolution of 0.1°, hourly
frequency and global coverage. We selected the variables for total
precipitation, 2 meters temperature, and volumetric soil water layers
between 0 and 100cm of depth (layer 1 to layer 3).

To derive a proxy of vegetation productivity, we used the product
MOD13A3 collection 6.1 from MODIS \citep{Didan2015}. It provides
vegetation indices (NDVI and EVI) at 1km of spatial resolution and
monthly frequency.

@@

\begin{minipage}[t]{\linewidth}

@@

\end{minipage}%
\newline
\begin{minipage}[t]{\linewidth}
